N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
Add latest edits to section 3

  \section{Introduction}
  \section{Overview of Project}
  % A high-level overview of what your project is about. This should answer the
  % following questions: What is the domain? Who are the users? What kinds of
  % things can those users do with your project?

@@

  There are many module structures instantiated in \texttt{tictactoe.sml}
  for the various kinds of state, actions and agents that we eventually want to
  use - such as \texttt{TttState} and \texttt{TttAction} for instance - but each will
  be used to implement the next kind of module.
  These module structures are bound to functors like \texttt{TttStateFn} which
  takes a module implementing a square matrix module (\texttt{SQUAREMATRIX})
  and returns a module that implements \texttt{TTTSTATE}.

@@

  We can then instantiate a structure like \texttt{TttExecRandom} that will run
  a game of \textit{Tic-tac-toe} by providing our \texttt{ExecFn} functor from
  \texttt{game.sml} with a module that implements \texttt{AGENT}.
  \texttt{ExecFn} then gives us a module that implements \texttt{EXEC}.

>>>>

  \section{Introduction}

  \section{Overview of Project}
  % A high-level overview of what your project is about. This should answer the
  % following questions: What is the domain? Who are the users? What kinds of
  % things can those users do with your project?

@@

  There are many module structures instantiated in \texttt{tictactoe.sml}
  for the various kinds of state, actions and agents that we eventually want to
  use - such as \texttt{TttState} and \texttt{TttAction} for instance - but each will
  be used to implement the next kind of module.
  These module structures are bound to functors like \texttt{TttStateFn} which
  takes a module implementing a square matrix module (\texttt{SQUAREMATRIX})
  and returns a module that implements \texttt{TTTSTATE}. The functors in
  \texttt{tictactoe.sml} effectively take a module structure that implements the
  previous module of the game pattern and produce the current (or next)
  modular piece.

@@

  We can then instantiate a structure (like \texttt{TttExecRandom} for example)
  that will run a game of \textit{Tic-tac-toe}
  To do so we provide our \texttt{ExecFn} functor from
  \texttt{game.sml} with a module that implements \texttt{AGENT}.
  \texttt{ExecFn} then gives us a module that implements \texttt{EXEC}.
